Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
make clearer that text refers to the movie

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the stimulus
structure, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% hypo
We hypothesized that due to the complex nature of a naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information accessible to a convential model-based
statistical analysis of BOLD fMRI data.
% we need a detailed description -> annotation
The current model-driven approach required a detailed annotation of the
occurence of relevant stimulus features.
% event counts ftw
The annotation of both types of naturalistic stimuli, a movie and its
audio-description, revealed the respective number of incidentally occurring
events to be similar to those of a conventional experimental paradigm used to
localize functional regions of interest.

>>>>

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in structure of
movies, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, katz1991film, mascelli1998five}.
% hypo
We hypothesized that due to the complex nature of the naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information accessible to a convential model-based
statistical analysis of BOLD fMRI data.
% we need a detailed description -> annotation
The current model-driven approach required a detailed annotation of the
occurence of relevant stimulus features.
% event counts ftw
The annotation of both types of naturalistic stimuli, a movie and its
audio-description, revealed the respective number of incidentally occurring
events to be similar to those of a conventional experimental paradigm used to
localize functional regions of interest.
